Untitled

### 2020-09-10 Rmd/brms_metric_selfing.Rmd
Preparing output

>>>>

# Model 2

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_data_m1.1_visits_self_all.RData")

#Model fit
pp_check(m1) + xlim(-100,2000)+ylim(0,0.02)
```

```{r, echo=FALSE, message=FALSE, cache=FALSE,  warning=FALSE, fig.width=3.5, fig.height=2, fig.align='center'}
setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1_visits_self_all.RData")
load("Data/RData/brms_data_m1_visits_self_all.RData")
c_e <- conditional_effects(m1.1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]

setwd("~/R_Projects/Reproductive traits") 
load("Data/RData/brms_m1.1_visits_self_all.RData")
load("Data/RData/brms_data_m1.1_visits_self_all.RData")

c_e <- conditional_effects(m1.1)
p1 <- plot(c_e, points=T,plot = FALSE)[[1]]
